---
title: "Alternative Assessment 2"
author: "Janice Chong See Wai (S2132420)"
date: '2022-06-02'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question(a)
#### Find and get a dataset from the datasets available within R.  Perform exploratory data analysis (EDA) and prepare a codebook on that dataset using a newer method in R. Label your work clearly on EDA and codebook.

##### In this question, I will be using the dataset called, "USArrests", which shows the Violent Crime Rates by US State.

### EDA
```{r}
# Get data, show the head of the data, get the summary of the data.
data("USArrests")
head(USArrests)
summary(USArrests)

```

### Boxplot 
I used boxplot because boxplot can show the distribution of the data of each variable in the five number summary that are minimum, first quartile, median, third quartile and maximum.

```{r}
# Create a boxplot to show the summary of the dataset.  
boxplot(USArrests,
        main = "Boxplot of Crime Cases in US.")
```

### Histogram 
I used histogram because histogram can show the frequency distribution of the data of each variable.

```{r}
# Plot histogram of each case.
hist(USArrests$Murder)
hist(USArrests$Assault)
hist(USArrests$UrbanPop)
hist(USArrests$Rape)
```

### Codebook
Make codebook by using a new method.
```{r}
# I called a package, "dataMaid". Then, I used the function "makeCodebook()" to make a code book.
# The code book will automatically be created as a new PDF document.

library(dataMaid)
makeCodebook(USArrests)

```

## Question(b)
### Demonstrate these FIVE (5) functions of dplyr for data manipulation:
###     i.	 filter ( )
###     ii.	 arrange ( )
###     iii. mutate ( )
###     iv.	 select ( ) 
###     v.	 summarise ( )
### You can create your own sensible dataset in certain context for this question with at least 15 observations (rows) and 4 features (columns) or you can get any suitable dataset online. Show the R code and provide a short explanation on what each function does for each produced output.

#### First, we call the dplyr package.

```{r}
# Calling dplyr package
library(dplyr)
```

### We will read a new csv dataset.

```{r}
data <- read.csv("supermarket_sales.csv")
head(data)
summary(data)
```

### i. filter() 
The filter() function is to provide a subset of a data frame while maintaing all rows of the specified conditions that we have made.

```{r}
# Filtering data with Branch A, Gross income > 15 and has a Rating of > 8
filtered <- filter(data, Branch=="A", gross.income>15, Rating>8)
head(filtered)

# Filtering data with Gender as Female, Payment with Ewallet and has a Rating of > 8
filtered <- filter(data, Gender=="Female", Payment=="Ewallet", 
                   Rating>8)
head(filtered)
```

### ii. arrange() 
The arrange() function is to arrange the dataset based on their column names.

```{r}
# We will arrange the dataset according to the payment method.
arranged <- arrange(data, Payment)
head(arranged)

```

### iii. mutate() 
The mutate() function creates a neew variable from existing data.

```{r}
# We will create a new variable called "Mean.Gross.Income" which contains the mean of gross income.
mutated <- mutate(data, mean.gross.income = mean(data$gross.income))
head(mutated)
```

### iv. select ( ) 
The select() function is used to select a particular column in a dataset.

```{r}
# We will select only the Invoice.ID, Branch, Product.line, gross.margin.percentage from the dataset.
selected <- select(data, Invoice.ID, Branch, Product.line, 
       gross.margin.percentage)
head(selected)
```

### v. summarise() 
The summarise ( ) function is to make a summary of a data frame by creating a new data frame but with lesser variables depending on what we want.

```{r}
# We will make a summary of the dataset that is group by Rating>8 and contains mean gross income.
data %>% group_by(Rating>8) %>% summarise(mean.gross.icome = mean(data$gross.income))
```




