---
title: "Lab_6_Challenge"
author: "Janice Chong See Wai"
date: '2022-04-21'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)

my_data <- read.csv("C:/Users/Janice/Documents/R/introdatascience/Lab/incomeData.csv")
```

### (a)	Choose the 2nd variable (state) from the original dataset combine it with its capital and its nickname. The state nickname is given below. Exclude form your original dataset “District of Columbia” row 9, as it is not a state in USA but its capital city.
```{r}
data <- select(my_data, State)
data <- filter(data, State != "District of Columbia")
data <- select(data, State)
data

vecNick <- c("Cotton State, Yellowhammer State", 
             "The Last Frontier",
             "Grand Canyon State", "Natural State",
             "Golden State", "Centennial State",
             "Nutmeg State, Constitution State",
             "First State, Diamond State", "Sunshine State",
             "Peach State, Empire State of the South",
             "Aloha State", "Gem State", 
             "Prairie State, Land of Lincoln","Hoosier State",
             "Hawkeye State, Corn State",
             "Sunflower State, Jayhawker State",
             "Bluegrass State", 
             "Pelican State, Creole State, Sugar State",
             "Pine Tree State","Free State, Old Line State",
             "Bay State, Old Colony State",
             "Wolverine State, Great Lake State",
             "North Star State, Gopher State, Land of 10,000 Lakes, Land of Sky-Blue Waters", "Magnolia State",
             "Show Me State",
             "Treasure State, Big Sky Country",
             "Cornhusker State, Beef State",
             "Silver State, Sagebrush State, Battle Born State",
             "Granite State","Garden State",
             "Land of Enchantment, Sunshine State",
             "Empire State",
             "Tar Heel State, Old North State",
             "Flickertail State, Sioux State, Peace Garden State",
             "Buckeye State","Sooner State","Beaver State",
             "Keystone State","Ocean State, Little Rhody",
             "Palmetto State","The Mount Rushmore State",
             "Volunteer State","Lone Star State",
             "Beehive State","Green Mountain State",
             "The Old Dominion, Mother of Presidents",
             "Evergreen State, Chinook State",
             "Mountain State",
             "Badger State, America’s Dairyland",
             "Equality State")
vecCap <- c("Montgomery","Juneau", "Phoenix","Little Rock",
            "Sacramento","Denver","Hartford","Dover",
            "Tallahassee","Atlanta","Honolulu","Boise",
            "Springfield","Indianapolis","Des Moines",
            "Topeka","Frankfort","Baton Rouge",
            "Augusta","Annapolis","Boston","Lansing",
            "Saint Paul","Jackson","Jefferson City","Helena",
            "Lincoln","Carson City","Concord","Trenton",
            "Santa Fe","Albany","Raleigh","Bismarck",
            "Columbus","Oklahoma City","Salem","Harrisburg",
            "Providence","Columbia","Pierre","Nashville",
            "Austin","Salt Lake City","Montpelier","Richmond",
            "Olympia","Charleston","Madison","Cheyenne")
df <- data.frame(Capital = vecCap, Nickname = vecNick)
df
df2 <- data.frame(data)
finalDf <- cbind(df2, df)
finalDf

```
### (b)	Translate all the THREE (3) column names in (a) to Malay language.
```{r}
finalDf <- rename(finalDf, Negeri = State, Ibu_Negeri = Capital, Nama_Samaran = Nickname)
finalDf
```
### (c)	Find the average income for each state from the year 2005 – 2015 and add the average income to the dataset. You may want to exclude 2002 to 2004 from the dataset.
```{r}
dataInc <- filter(my_data, State != "District of Columbia")
dataInc
dataInc <- select(dataInc,Y2005:Y2015)
dataInc <- cbind(df2, dataInc)
dataInc 

dataInc$Average <- rowSums(dataInc[ ,
                                  c(2:12)])/(ncol(dataInc)-1)
dataInc


```
### (d)	Extract rows based on (c) for top 5 highest income states & top 5 lowest income states
```{r}

top5 <- dataInc %>% arrange(desc(Average)) %>% slice(1:5)
top5 <- select(top5, State, Average)
top5

bottom5 <- dataInc %>% arrange(Average) %>% slice(1:5) %>% select(State, Average)
#bottom5 <- select(bottom5, State, Average)
bottom5
```

